Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-11-30 inst/paper/main.tex
minor

@@

\subsubsection{Operation Mix}

The JavaScript paper reported on the operation mix within \evals. This
means the proportion of read, write, and call bytecodes performed by
the JavaScript interpreter. They found that some web pages were
creating objects more frequently and writing into their fields. In R,
nearly every operation performed in the interpreter is a function
call. We observe 2.9G calls and, of those 125M happen inside \eval
(there are 463M native calls, of which only 31M are in \eval).

{\bf there is no good reason for not counting reads and writes, we can...}

%% ...The following is fluff ...

%% Qualitatively, we observe all kinds of operations being executed
%% inside \eval calls, from numerical computing for statistical
%% modeling to reflection and metaprogramming for implementing DSLs.
%% Even testing frameworks such \c{genthat} heavily rely upon \eval to
%% execute test code snippets. The core R implementation is rife with
%% uses of \eval for mundane things like accessing default values of
%% formal parameters and in statistical packages for computation.

@@

\noindent \emph{Library}, \emph{Typeof} and \emph{Try} are all barely
used mostly because the language provides dedicated features for it.
The few calls in Library pattern come mostly from file loading
functions such as \c{source} and \c{sys.source}.
%
\noindent \emph{Read} pattern in JavaScript represented mostly an incorrect

access to an object's property or local variable both replaceable by
JavaScript core functions. In the case of R there are \PatternReadRnd
read \eval calls (\PatternReadRatio). They come from calls like
\c{subset(airquality, select = Temp)} where the variable \c{Temp} will
be evaluated in the \c{airquality} data frame.

@@

\subsubsection{How much code is executed inside eval}
- measure number of operations inside eval and outside eval.
- this is useful because if analyzers treat eval as a nop, they may miss X\% of the code.

\subsubsection{Does eval create observable side-effects}
- measure number of reads and writes by eval outside of its ``bubble''.
- Since R is lazy, even reads can cause promise evaluation and hence, side-effects.
- Look at writes to non-local scopes. Compare with total number of writes for
reference?
- Categorize side-effects between env passed to eval and other envs.

@@

In JavaScript, the provenance of the string passed into \eval is a matter of
concern as \eval can be used to breach the security of websites. The main
danger comes from string that were obtained from external sources. If they
are allowed to flow into an \eval, then an attacker could hijack the
program.

{\bf what have they found...}

@@

\begin{table}[htbp]{%} \resizebox{\columnwidth}{!}{%
    \centering
    \begin{tabular}{c|c|c|c}
        \hline
        \multicolumn{2}{c|}{Core} & \multicolumn{2}{|c}{Packages}  \\
        \hline
        Environment Class & Eval Calls \% & Environment Class & Eval Calls \% \\
        \hline
        \CoreEnvClassA & \CoreProportionA & \PackagesEnvClassA &  \PackagesProportionA\\
        \CoreEnvClassB & \CoreProportionB & \PackagesEnvClassB &  \PackagesProportionB\\
        \CoreEnvClassC & \CoreProportionC & \PackagesEnvClassC &  \PackagesProportionC\\
        \CoreEnvClassD & \CoreProportionD & \PackagesEnvClassD &  \PackagesProportionD\\
        \CoreEnvClassE & \CoreProportionE & \PackagesEnvClassE &  \PackagesProportionE\\
        \hline
    \end{tabular}} \label{tab:environments}
\caption{Environments in terms of eval calls.}
\end{table}

>>>>

The previous section gave a quantitative view of the usage of \eval;
in this section we try to elucidate \emph{what} it does.

@@

@@

\noindent \emph{Library}, \emph{Typeof} and \emph{Try} are all barely
used mostly because the language provides dedicated features for it.
The few calls in Library pattern come mostly from file loading
functions such as \c{source} and \c{sys.source}.
%
\noindent
\emph{Read} pattern in JavaScript represented mostly an incorrect
access to an object's property or local variable both replaceable by
JavaScript core functions. In the case of R there are \PatternReadRnd
read \eval calls (\PatternReadRatio). They come from calls like
\c{subset(airquality, select = Temp)} where the variable \c{Temp} will
be evaluated in the \c{airquality} data frame.

@@

\subsubsection{How much code is executed inside eval}
- measure number of operations inside eval and outside eval.

- this is useful because if analyzers treat eval as a nop, they may
miss X\% of the code.

\subsubsection{Does eval create observable side-effects}
- measure number of reads and writes by eval outside of its ``bubble''.

- Since R is lazy, even reads can cause promise evaluation and hence,
side-effects.

- Look at writes to non-local scopes. Compare with total number of
writes for reference?

- Categorize side-effects between env passed to eval and other envs.

@@

@@

\begin{table}[htbp]{ \centering
\begin{tabular}{c|c|c|c}\hline
\multicolumn{2}{c|}{Core} & \multicolumn{2}{|c}{Packages}  \\\hline
Environment Class & Eval Calls \% & Environment Class & Eval Calls\\\hline
\CoreEnvClassA & \CoreProportionA & \PackagesEnvClassA &  \PackagesProportionA\\
\CoreEnvClassB & \CoreProportionB & \PackagesEnvClassB &  \PackagesProportionB\\
\CoreEnvClassC & \CoreProportionC & \PackagesEnvClassC &  \PackagesProportionC\\
\CoreEnvClassD & \CoreProportionD & \PackagesEnvClassD &  \PackagesProportionD\\
\CoreEnvClassE & \CoreProportionE & \PackagesEnvClassE &  \PackagesProportionE\\\hline
\end{tabular}} \label{tab:environments}
\caption{Environments in terms of \eval calls}
\end{table}
